PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-11 qfenv_paper/qf_environment.tex
updated plots and text

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.

\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection. Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample. Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
$0.0375-0.145$ &High           &5470                       &4501                           \\
               &Low            &5419                       &8927                           \\
               &               &                       &                           \\ \hline
$0.2-0.4$      &High           &322                    &583                           \\
               &Low            &768                    &2516                           \\
               &               &                       &                           \\ \hline
$0.4-0.6$      &High           &350                       &675                           \\
               &Low            &871                       &2385                           \\
               &               &                       &                           \\ \hline
$0.6-0.8$      &High           &347                       &430                           \\
               &Low            &833                       &1847                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

@@

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.  
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDGE EFFECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey. For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.

@@

\subsection{Evolution of the Stellar Mass Function in Different Environments} \label{sec:smfevol}
In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The width of the SMFs represent the sample variance uncertainties.
%%%%%%% REWRITE AFTER REVISED SMF RESULTS
%As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

%Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. 
In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$). In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF. In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee. For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end. Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.

@@

%We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).

From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.

@@

@@

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

>>>>

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection. Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample. Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
$0.05-0.12$ &Low           &12859                       &14443                           \\
               &High            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2-0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4-0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6-0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \bigskip 
    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}. The subsamples are classified based on environment and star formation rate. The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. 
  \end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

@@

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment. The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. We also adjusted the environment classification thresholds for these analyses. The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDGE EFFECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey. For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.

@@

\subsection{Evolution of the Stellar Mass Function in Different Environments} \label{sec:smfevol}
In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The width of the SMFs represent the sample variance uncertainties.

While a detailed comparison of the SMFs in each panel for different epochs are complicated due to the different stellar mass completeness limits, we present some notable trends in each panel. In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$). In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF. In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee. For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end. Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.

@@

While our mass complete subsample coupled with robust environment measurement allows us to compare SMF evolution for each of our subsamples over $z < 1.0$, we caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \label{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins. The width of the quiescent fraction represents the uncertainty from sample variance. As done in Section \ref{sec:smfevol} for the stellar mass function, we use the standard jack-knife technique

@@

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \label{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

@@
